On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-03-22 Code/Visualizations.Rmd
Manuscript Update 3/22

>>>>

```{r}
plot(c(0, 1200), c(600, 1400), type= "n", xlab = "", ylab = "")
xleft = rep(c(200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100), times = 4)
ybottom = rep(c(1200, 900, 600, 0), each = 10)
xright = rep(c(300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200), times = 4)
ytop = rep(c(1400, 1100, 800, 200), each = 10)
rect(xleft = xleft, ybottom = ybottom, xright = xright, ytop = ytop)
rect(xleft = c(200, 500, 900), ybottom = c(1200, 900, 600), xright = c(500, 800, 1200), 
     ytop = c(1400, 1100, 800), col= rgb(1,0,0,alpha=0.25))
x = rep(c(250, 350, 450, 550, 650, 750, 850, 950, 1050, 1150), times = 4)
y = rep(c(1300, 1000, 700, 100), each = 10)
labels = rep(c('X1', 'X2', 'X3', 'X4', 'X5', 'X6', '...', 'Xn-2', 'Xn-1', 'Xn'), times = 4)
text(x=x, y=y, labels=labels)
text(x=100, y=1300, labels='Block 1')
text(x=100, y=1000, labels='Block 2')
text(x=100, y=700, labels='Block n/l')
```

```{r}
plot(c(0, 1200), c(0, 1400), type= "n", xlab = "", ylab = "")
rect(xleft = xleft, ybottom = ybottom, xright = xright, ytop = ytop)
rect(xleft = c(200, 300, 400, 200, 1100), ybottom = c(1200, 900, 600, 0, 0), xright = c(500, 600, 700, 400, 1200), ytop = c(1400, 1100, 800, 200, 200), col= rgb(1,0,0,alpha=0.25))
labels = rep(c('X1', 'X2', 'X3', 'X4', 'X5', 'X6', '...', 'Xn-2', 'Xn-1', 'Xn'), times = 4)
text(x=x, y=y, labels=labels)
text(x=100, y=1300, labels='Block 1')
text(x=100, y=1000, labels='Block 2')
text(x=100, y=700, labels='Block 3')
text(x=100, y=100, labels='Block n')
```

### 2023-03-22 Manuscript/manuscript.tex
Manuscript Update 3/22

@@

@@

@@

\jy{Paragraph: bascic percentiles; use the terminologies in the literature.}

@@

@@

Block bootstrap is a method that can be used to estimate a parameter of
serially dependent data. Suppose that one wants to estimate a parameter or
parameters $\theta$ of a population. The first step is to generate a sample of
length $n$ from the population. An estimate of the parameter
$\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate
$\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean
$\bar\theta_n^*$ of many replicate $\hat\theta_n^*$ can also be computed.
Lastly, for each $\hat\theta_n^*$, $\delta^* = \hat\theta_n^* -
\bar\theta_n^*$ can be computed.

In basic bootstrap procedure, the new pseudo-sample of size $n$ would be
created by simply resampling observations from the original sample with
replacement. However, in the case of a time series, in order to account for
the temporal dependence, the time series can be split into blocks, typically
of the same size. The block should be of size $l$ large enough for each
pseudo-sample to exhibit some temporal dependence, yet small enough for there
to be some variability between each pseudo-sample. Ideally, as $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

The designer of the study can choose whether the blocks overlap or not. If the
blocks do not overlap, it is called non-overlapping or non-moving block
bootstrap. In this case, blocks are resample randomly from the set of all
non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
must always be true. In this case, a set of $n / l$ non-overlapping blocks of
size $l$ is constructed from the original sample. Each bootstrapped
pseudo-sample is created by sampling $n / l$ blocks with replacement from the
same set.

If the blocks do overlap, it is called overlapping or moving block bootstrap.
In this case, blocks are resampled randomly from the set of all possible
blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
condition. The set of available blocks is created by iterating through each
observation $i$ in the original sample and adding to the set the block of size
$l$ that begins with $i$. This set can limited to blocks that end with an
$i <= n$, meaning that $n - l + 1$ blocks are availabe to resample from, or it
can be expanded to include blocks that ``wrap around'': in
other words, blocks that end with a lesser index than the index they began
with, meaning that $n$ blocks are available to resample from. If $l \vert n$,
a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
from the set with replacement to create a new pseudo-sample of size $n$. If
$l does not divide n$, the last block selected will be reduced in size so that
the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The set of available was not limited as
described above.

An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This
procedure can be repeated many times to create a distribution of
$\hat\theta_n^*$.

In this study, 1000 $\hat\theta_n^*$ were created for one simulation of block
bootstrap estimation. Using this distribution of $\hat\theta_n^*$, several
variants of a $1 - \alpha$/2 \% confidence interval for the parameter can be
constructed. The most simplistic method for constructing this interval is the
basic percentile confidence interval. For a parameter $\theta$, the percentile
$1 - \alpha$/2 \% confidence interval takes the form: 
\[ [\hat\theta_{n, \alpha/2}^*, \hat\theta_{n, 1 - \alpha/2}^*].\]

This interval works well when attempting to recover the mean and
standard deviation of a temporally dependent process, but its coverage of
the temporal dependence deteriorates as $n$ increases. A potential solution to
this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
the distribution of $\delta^*$ should be considered. For a parameter $\theta$,
the $\hat{\theta}_{n}$-centered $1 - \alpha$/2 \% confidence interval takes
the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]

An alternative method is a $BC_a$ interval centered around $\hat{\theta}_{n}$.
For a parameter $\theta$, the $BC_a$ $1 - \alpha$/2 \% confidence interval
takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\] 
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^* < \bar\theta_n^*$, and $a$ is the skewness (computed using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we genrated 1000
replicates. For each replicate, we constructed three 95\% block bootstrap
confidence intervals for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 1000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size \jy{size? also it was overlapping blocks. Describe the details here.}
The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi}.

@@

@@

Each of these 9 intervals either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% confidence intervals constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% confidence interval of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

The figures below which are grouped by the target $\theta$  were created using
the R ggplot2 package \citep{ggplot2}.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{At $\phi = -.4, -.2$, all intervals seem to cover $\mu$ correctly
    as low as $n = 100$. At $\phi = 0$, an $n$ of 500 seems large enough to
    cover $\mu$ acceptably regardless of interval type. At $\phi = .2$,
    $n = 300$ seems to be sufficient to appropriately recover $\mu$ for all
    intervals. A much larger $n$ seems to be necessary to recover $\mu$ at a
    $\phi$ as high as $.4$.}
  \label{fig:plot_mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{At $\phi = -.4$, the percentile and the
    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
    $n = 400$, whereas the $BC_a$ interval undercovered $\mu$ for all $n$
    observed. At $\phi = -.2$, the percentile and the
    $\hat{\theta}_{n}$-centered intervals recovered $\mu$ well as low as
    $n = 500$, but the $BC_a$ coverage rates were lower.}
  \label{fig:plot_sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{}
  \label{fig:plot_phi}
\end{figure}

@@

The motivation for the study is the idea that block bootstrap procedure will
perfectly estimate a parameter of a time series given an infinitely large
sample. The goal for this study was to find what is a good enough finite
sample length for block bootstrap estimation to recover the parameter of a
time series at an acceptable rate. Again, this relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile $BC_a$ intervals exhibited coverage deterioration as $n$
increased. When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around 500 may be
necessary to estimate $\mu$, and an $n$ of around 400 may be necessary to
estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
This information could prove to be useful for researching using block bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap intervals
constructions that would more appropriately recover the parameters of a time
series. One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as an MA process.

@@

>>>>

The designer of the study can choose whether the blocks overlap or not. If the
blocks do not overlap, it is called non-overlapping or non-moving block
bootstrap. In this case, blocks are resample randomly from the set of all
non-overlapping blocks of size $l$. For non-moving block bootstrap, $l \vert n$
must always be true. In this case, a set of $n / l$ non-overlapping blocks of
size $l$ is constructed from the original sample. The set would take the form:
$\{[X_1, ..., X_l], [X_{l+1}, ..., X_{2l}], ..., [X_{n-l+1}, X_n]\}$. Each
bootstrapped pseudo-sample is created by sampling $n / l$ blocks with
replacement from the same set.

@@

If the blocks do overlap, it is called overlapping or moving block bootstrap.
In this case, blocks are resampled randomly from the set of all possible
blocks of size $l$. For moving block bootstrap, $l \vert n$ is not a necessary
condition. The set of available blocks is created by iterating through each
observation $i$ in the original sample and adding to the set the block of size
$l$ that begins with $i$. This set can limited to blocks that end with an
$i <= n$, meaning that $n - l + 1$ blocks are available to resample from. This
set takes the form:
$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_{n-l+1}, X_n]\}$. 
The set can also include blocks that ``wrap around'': in
other words, blocks that end with a lesser index than the index they began
with, meaning that $n$ blocks are available to resample from. This set takes
the form:
$\{[X_1, ..., X_l], [X_2, ..., X_{l+1}], ..., [X_n, X_{l-1}]\}$.
If $l \vert n$,
a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks
from the set with replacement to create a new pseudo-sample of size $n$. If
$l does not divide n$, the last block selected will be reduced in size so that
the final size of the pseudo-sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The larger set of available blocks was used.

@@

The block should be of size $l$ large enough for each
pseudo-sample to exhibit some temporal dependence, yet small enough for there
to be some variability between each pseudo-sample. Ideally, as $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

@@

\jy{Paragraph: basic percentiles; use the terminologies in the literature.}

In this study, 1000 $\hat\theta_n^{(b)}$ were created for one simulation of
block bootstrap estimation. Using this distribution of $\hat\theta_n^{(b)}$,
several variants of a $1 - \alpha$/2 \% confidence interval for the parameter
can be constructed. The most simplistic method for constructing this interval
is the basic percentile confidence interval. For a parameter $\theta$, the
percentile $1 - \alpha$/2 \% confidence interval takes the form:
\[ [\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}].\]

This interval works well when attempting to recover the mean and
standard deviation of a temporally dependent process, but its coverage of
the temporal dependence deteriorates as $n$ increases.

@@

A potential solution to
this issue is to center the intervals around $\hat{\theta}_{n}$. To do this,
the distribution of $\delta^*$ should be considered. For a parameter $\theta$,
the $\hat{\theta}_{n}$-centered $1 - \alpha$/2 \% confidence interval takes
the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]

@@

An alternative method is a $BC_a$ interval centered around $\hat{\theta}_{n}$.
For a parameter $\theta$, the $BC_a$ $1 - \alpha$/2 \% confidence interval
takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]
$\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\]
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x^2 = 1$, the variance of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, \ldots, 1000\}$. In each configuration, we generated 1000
replicates. For each replicate, we constructed three 95\% block bootstrap
confidence intervals for each parameter as described in the last section, and
estimated their actual coverage rates along with their 95\% confidence
intervals from the 1000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section.
\jy{size? also it was overlapping blocks. Describe the details here.}
The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
these figures were generated using the using
the R ggplot2 package \citep{ggplot2}.

Each interval either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% confidence intervals constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% confidence interval of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

- For mu, performance looks about the same regardless of interval type.
- When phi is negative, n = 100 seems large enough.
- When phi is zero, n = 500 is large enough.
- When phi is 0.2, n = 300
- When phi is 0.4, a much larger n seems to be necessary

Based on \ref{fig:mu}, performance is
about the same for the three interval types studied. When $\phi < 0$,
$n = 100$ seems to  be large enough to cover $\mu$ at the nominal rate. When
$\phi = 0$, or in other other words, the sample is from a normal distribution,
$n = 500$ seems to be large enough to cover $\mu$ at the nominal rate. Samples
from processes with $\phi > 0$ appear to require a larger $n$ than samples from
processes with $\phi < 0$. When $\phi = 0.2$, $n = 300$ seemed to be necessary
for adequate performance, and when $\phi = 0.4$, an even larger $n$ appeared
to be necessary to properly cover $\mu$. It is rare for $\phi$ to be so high,
so in most cases, if $\phi$ is unknown, a sample of $n \geq 500$ should be
used when the target parameter is $\mu$.

- For sigma, coverage looks lower for BCa, whereas percentile and centered
look about the same.
- For percentile and centered intervals, n = 400 looks enough when phi = -0.4.
- When phi = -0.2, n = 500 seems to be necessary for percentile and centered
intervals.
- When phi = 0, n = 400 seems to be necessary for percentile and centered
intervals.
- When phi = 0.2, n = 300 seems to be necessary...
- When phi = 0.4, n = 400 seems to be necessary...

Based on \ref{fig:sigma}, coverage is
notably lower for $BC_a$ intervals, but $\hat{\theta}_{n}$-centered intervals
and basic intervals have similar performance. For these two interval types,
$n = 500$ seems to be necessary to cover $\sigma$ at the nominal rate when
$\phi < 0$. If $\phi = 0$, $n = 400$ seems to large enough to cover $\sigma$ at
the nominal rate. If $\phi = 0.2$, $n = 300$ seems large enough, but if the
process has a greater $\phi$ of $0.4$, $n = 400$ may be necessary. It is more
common for $\phi$ to be $> 0$ in applied analysis, so in most cases, if $\phi$
is unknown, using a sample of $n \geq 400$ should be sufficient for estimation
of $\sigma$.

- BCa and percentile deteriorate in coverage as n increases, except for when
phi = 0.
- BCa coverage is very bad when absolute value of phi is high.
- Percentile coverage is not as bad
- n = 200 seems to be enough for centered interval, regardless of phi.

When block bootstrap is used to estimate $\phi$ using $BC_a$ and percentile
intervals, the assumption that coverage rates asymptotically approach the
nominal rate as $n$ increases appears to be invalid based on \ref{fig:sigma}.
The $BC_a$ interval performs very poorly and deteriorates more noticeable
when the absolute value $\phi$ gets
higher, but even when $\phi = 0$, $\phi$ is still undercovered for $n$ as high
as $700$. Like the $BC_a$ interval, the percentile interval deteriorates in
coverage when $\phi$ is high, although the coverage is not as low.
Interestingly, when $\phi = 0$, the percentile interval appears to actually
over-cover $\phi$. These results suggest that $BC_a$ and basic percentile
block bootstrap intervals should not be used estimate temporal dependence
factors of time series. On the other hand, $\hat{\theta}_{n}$-centered
intervals seem to recover $\phi$ correctly as long as $n >= 200$, and this
appears to be true regardless of $\phi$, although a greater $\phi$ may result
in a decline in performance.

@@

To summarize, the interval type chosen should be based on the target parameter.
For estimating $\mu$, any of the three interval types can be used, but for
$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
for $\phi$. When estimating
$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
$\phi$, $n = 200$ is large enough when using the correct type of interval.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_mu}
  \caption{Plots of $\mu$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Plots of $\sigma$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_phi}
  \caption{Plots of $\phi$ coverage rates for each interval type and $\phi$
    combination. The orange dotted line represents the 95\% nominal coverage
    rate. The error bars represent a 95\% confidence interval for the coverage
    proportion out of 1000 replications for each $n$. Results from $n$
    ranging from 100-700 were recorded.}
  \label{fig:phi}
\end{figure}

@@

Block bootstrap method is a useful method for estimating parameters of a time
series: from simple parameters like the mean to temporal dependence factors.
The motivation for the study is the idea that block bootstrap procedure will
perfectly estimate a parameter of a time series given an infinitely large
sample. The goal for this study was to find what is a good enough finite
sample length for block bootstrap estimation to recover the parameter of a
time series at an acceptable rate. Again, this relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile $BC_a$ intervals exhibited coverage deterioration as $n$
increased. When using $\hat{\theta}_{n}$-centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around 500 may be
necessary for common practice to estimate a simple parameter like $\mu$, and
an $n$ of around 400 may be necessary to
estimate $\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to
estimate these parameters. When $\phi$ was negative, a $n$ of around 100 was
sufficient to estimate $\mu$. However, in real world applications, $\phi$ is
more commonly found to be positive, so a larger $n$ is more likely to be
necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods.
This information could prove to be useful for researching using block bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap intervals
constructions that would more appropriately recover the parameters of a time
series. One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as an MA process.

@@

BBOB
